Numerical modelling of the Cordilleran ice sheet

### 2014-08-24 kappa.tex
Add space for Swedish abstract.
Reposition floats.
Add missing preamble information.

% Document properties
%\title{Numerical modelling of the Cordilleran ice sheet}
%\author{Julien Seguinot}
\thesistitle{Numerical modelling of the Cordilleran ice sheet}
\runningtitle{Numerical modelling of the Cordilleran ice sheet}
\candidate{Julien Seguinot}
\runningauthor{J. Seguinot}
\pubyear{2014}
\department{Department of Physical Geography and Quaternary Geology}
\university{Stockholm University}
\printed{Universitetsservice US-AB, 2014.}
%\issn{}
%\isbn{}
%\coverpic{Richard Swan. \textsf {www.richardswan.com}. Back cover portrait: Louise Tränk.}
%\layout{Summary and Papers IV \& V: Alistair Auffret based on  \LaTeX~templates by Rickard Petterson. Published papers typeset by respective publishers, reprinted with permission. Graphics created using \textsf{Inkscape}, \textsf{R} and \textsf{OpenOffice Draw}.}

@@

%\begin{keyword}
%\end{keyword}
%\begin{svabstract}
%\end{svabstract}

@@

Vectors are identified by bold arrow symbols ($\vv$) and second-order tensors by bold symbols ($\CST$), while scalars use a normal font ($s$). The divergence of a vector field is written $\div{\vv}$, and $\grad{s}$ denotes the gradient of a scalar field. The divergence of a tensor field is characterised by $\tdiv{\CST}$ and the gradient of a vector field by $\tgrad{\vv}$. The race of a tensor $\CST$ is written $\tr(\CST)$. Parameter values are summarised in \cref{tab:params}.

\newpage  %FIXME temporary fix

@@

% ======================================================================
\section{Results summary}
% ======================================================================

>>>>

% Document properties
\thesistitle{Numerical modelling of the Cordilleran ice sheet}
\runningtitle{Numerical modelling of the Cordilleran ice sheet}
\candidate{Julien Seguinot}
\runningauthor{J. Seguinot}
\pubyear{2014}
\department{Department of Physical Geography and Quaternary Geology}
\university{Stockholm University}
\issn{1653-7211}
\isbn{978-91-7447-973-7}
\coverpic{Numerical reconstruction of the Cordilleran ice sheet at the Last
          Glacial Maximum. Bedrock topography, ice surface topography, ice
          surface velocity, and frozen bed areas.}
\layout{Julien Seguinot based on {\LaTeX} templates by Rickard Petterson
        (summary) and Copernicus Publications (Paper~IV). Published papers
        typeset by Copernicus Publications (Paper~I) and the International
        Glaciology Society (Papers~II and~III). Graphics created using
        matplotlib, cartopy, {\LaTeX} and Inkscape.}
\printed{Universitetsservice US-AB, Stockholm, Sweden, 2014.}

@@

%\begin{keyword}
%\end{keyword}

\begin{svabstract}

Hej!
Här kommer sammanfattning på svenska. Här kommer sammanfattning på svenska.
Här kommer sammanfattning på svenska. Här kommer sammanfattning på svenska.
Här kommer sammanfattning på svenska. Här kommer sammanfattning på svenska.
Här kommer sammanfattning på svenska. Här kommer sammanfattning på svenska.
Här kommer sammanfattning på svenska. Här kommer sammanfattning på svenska.
Här kommer sammanfattning på svenska. Här kommer sammanfattning på svenska.
Här kommer sammanfattning på svenska. Här kommer sammanfattning på svenska.
Här kommer sammanfattning på svenska. Här kommer sammanfattning på svenska.

\end{svabstract}

%\begin{svkeyword}
%\end{svkeyword}

@@

Vectors are identified by bold arrow symbols ($\vv$) and second-order tensors
by bold symbols ($\CST$), while scalars use a normal font ($s$). The divergence
of a vector field is written $\div{\vv}$, and $\grad{s}$ denotes the gradient
of a scalar field. The divergence of a tensor field is characterised by
$\tdiv{\CST}$ and the gradient of a vector field by $\tgrad{\vv}$. The race of
a tensor $\CST$ is written $\tr(\CST)$. Parameter values are summarised in
\cref{tab:params}, \cpageref{tab:params}.

@@

% ======================================================================
\newpage
\section{Results summary}
% ======================================================================
